Cultural Transmission Can Explain the Evolution of Cooperation

### 2020-07-30 ms/main.tex
added todo
edit appendix A

Here, the third equilibrium is
\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) },
\end{equation} 
and the cost boundaries are
\begin{equation}\begin{aligned}
\gamma_1(\alpha=0) = \frac{T_B - T_A}{1-T_B}, \quad
\gamma_2(\alpha=0) = \frac{(1+b) (T_A - T_B)}{1-T_B}.
\end{aligned}\end{equation}
If $T_A>T_B$ then $\gamma_1(\alpha=0)<0<\gamma_2(\alpha=0)$.
So cooperation cannot increase from rarity, but it can fix if $c<\gamma_2(\alpha=0)$.
If $T_A<T_B$ then $\gamma_2(\alpha=0)<0<\gamma_1(\alpha=0)$.
So cooperation cannot fix, but if $c<\gamma_1(\alpha=0)$ then it can increase from rarity to a stable coexistence at $\tilde{p}^*(\alpha=0)$.
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{} \label{sec:appendixB}
We want to find the frequency of juveniles with phenotype $A$ in next generation $\hat{p}'$ as a function of frequency
of juveniles with phenotype $A$ in the current generation $\hat{p}$.
We start from eq.~\ref{eq:horizontal},
\begin{equation}\label{eq:appendix_b_1}
  \hat{p}' = v \tilde{p}' + (1-v) p'
  \end{equation}
Substituting $p'$ using eq.~\ref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ using eq.~\ref{eq:nextgen_parents_simplified}, we have
\begin{equation}\label{eq:appendix_b_2}
  \begin{aligned}
  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
\end{aligned}
\end{equation}
where $\bar{w} = 1 + \hat{p}(b-c)$.

We define $f(\hat{p})$ to be
\begin{equation} \label{eq:appendix_b_3}
\begin{aligned}
      f(\hat{p}) &= \bar{w}(\hat{p}' - \hat{p})
\end{aligned}
\end{equation}
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we simplify \autoref{eq:appendix_b_3} to 
\autoref{eq:general_case_polynomial} and \autoref{eq:polynomial_coefficients}.

>>>>

Here, the third equilibrium is
\begin{equation} \label{eq:vert_hori_alpha0_equilibrium}
\tilde{p}^*(\alpha=0) = \frac{c(1-T_B) - (T_A-T_B)}{b (T_A-T_B) },
\end{equation} 
and the cost boundaries are
\begin{equation}\begin{aligned}
\gamma_1(\alpha=0) = \frac{T_B - T_A}{1-T_B}, \quad
\gamma_2(\alpha=0) = \frac{(1+b) (T_A - T_B)}{1-T_B}.
\end{aligned}\end{equation}
If $T_A>T_B$ then $\gamma_1(\alpha=0)<0<\gamma_2(\alpha=0)$.
So cooperation cannot increase from rarity, but it can fix if $c<\gamma_2(\alpha=0)$.
If $T_A<T_B$ then $\gamma_2(\alpha=0)<0<\gamma_1(\alpha=0)$.
So cooperation cannot fix, but if $c<\gamma_1(\alpha=0)$ then it can increase from rarity to a stable coexistence at $\tilde{p}^*(\alpha=0)$.
%TODO add "effective cost" argument: c<TA-TB/(1-TB) <=> 1-(1-c)(1-TB)<TA.
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{} \label{sec:appendixB}
We want to find the frequency of juveniles with phenotype $A$ in next generation $\hat{p}'$ as a function of frequency
of juveniles with phenotype $A$ in the current generation $\hat{p}$.
Starting from \autoref{eq:horizontal},
\begin{equation}\label{eq:appendix_b_1}
  \hat{p}' = v \tilde{p}' + (1-v) p',
\end{equation}
we substitute $p'$ using \autoref{eq:nextgen_adults_slimpify} and $\tilde{p}'$ using \autoref{eq:nextgen_parents_simplified}, we have
\begin{equation}\label{eq:appendix_b_2}
  \begin{aligned}
  \hat{p}'  = & \frac{v}{\bar{w}}\left\{\hat{p}^2(1+b-c)\left[1-(1-\hat{p})(1-\alpha)T_B)\right]\right\} \\
  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1-c)\left[ \hat{p}(1-\alpha)T_B + 1 - T_B \right] \right\} \\
  & + \frac{v}{\bar{w}}\left\{ \hat{p}(1-\hat{p})(1+b)\left[\hat{p}(1-\alpha) + \alpha \right]T_A \right\} \\
  & + \frac{v}{\bar{w}}(1-\hat{p})^2\hat{p}(1-\alpha)T_A \\
  & + (1-v)\hat{p}^2(T_B-T_A) + (1-v)\hat{p}(1+T_A-T_B),
\end{aligned}
\end{equation}
where $\bar{w} = 1 + \hat{p}(b-c)$. 
We define $f(\hat{p})$ as
\begin{equation} \label{eq:appendix_define_f}
\begin{aligned}
      f(\hat{p}) &= \bar{w}(\hat{p}' - \hat{p})
\end{aligned}
\end{equation}
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we simplify \autoref{eq:appendix_define_f} to 
eqs.~\ref{eq:general_case_polynomial}-\ref{eq:polynomial_coefficients}.
